GSS Education Analysis (Working Title)

### 2023-03-12 outputs/paper/paper.qmd
add graphs

>>>>

```{r}

#| echo: false
#| warning: false
#| label: fig-20
#| fig-cap: "degree"

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = happy, fill = degree)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "happy",
       x = "number")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```
